Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
describe the device types in 4a, leave comments for @nicolasfara

In this example, we exercise the framework on a real-world testbed
located in a laboratory.
%
In particular,
we want to avoid situations in which too many people are too close to each other in the same room for safety reasons.
%
To do so,
we equip each person with a wearable device that is able to detect the distance from other simialr devices via Bluetooth.
%
For the sake of simplicity,
in the experiment we relied on smartphones to emulate wearables,
and we used \meta{
    NICOLAS please write here (within meta, so that it remains blue)
    what you used to measure the signal strenght and estimate the distance.
    Even formulas, calibration procedures, and stuff
}
%
In our case the warning was issued through a monitor,
whose color was set to tones ranging from green to red depending on the average distance among people:
the shorter the distance, the more red the tone.
%
\Cref{fig:crowd-alert} shows a representation of the scenario.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in \Cref{sec:small-scale-crowd-alert}.
        graph dots represent wearables,
        and arcs lenghts represent the distance between them.
        %
        The rectangle at the bottom represents the monitor.
        %
        The closer the wearables are, the higher is the alert level
        (reddish tones).
        %
        \meta{NICOLAS riduci lo spazio vuoto fra i tre casi, così da guadagnare spazio. La legenda potrebbe essere messa sotto o sopra per guadagnarne di ulteriore}
    }
    \label{fig:crowd-alert}
\end{figure}
%
The system is composed of two kind of devices: \emph{wearable} and \emph{laboratory}.
%
The former represents the wearable devices that is worn by the people, and consists of the following pulverized components:
$\beta$, $\chi$, and $\sigma$.
%
The \emph{behaviour} ($\beta$) component is responsible for converting the raw data from the sensor into the distance
between the device and the others; the \emph{sensors} ($\sigma$) component is responsible for perceiving the other devices and
the \emph{communication} ($\chi$) component is responsible for sending the data to the alert system.
%
The latter represents the alert system and consists of the following pulverized components:
$\beta$, $\kappa$, $\chi$, and $\alpha$.
%
The \emph{behaviour} ($\beta$) component is responsible for evaluating the meand distance between the devices,
the \emph{actuators} ($\alpha$) is responsible for triggering the alarm showing a color in the screen,
and the \emph{communication} ($\chi$) component is responsible for receiving the data from the wearable devices.

>>>>

In this example, we exercise the framework on a real-world testbed
located in a laboratory.
%
In particular,
we want to avoid situations in which too many people are too close to each other in the same room for safety reasons.
%
To do so,
we equip each person with a wearable device that is able to detect the distance from other simialr devices via Bluetooth.
%
For the sake of simplicity,
in the experiment we relied on smartphones to emulate wearables,
and we used \meta{
    NICOLAS please write here (within meta, so that it remains blue)
    what you used to measure the signal strenght and estimate the distance.
    Even formulas, calibration procedures, and stuff
}
%
In our case the warning was issued through a monitor,
whose color was set to tones ranging from green to red depending on the average distance among people:
the shorter the distance, the more red the tone.
%
\Cref{fig:crowd-alert} shows a representation of the scenario.
%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/crow-laboratory-demo.drawio.pdf}
    \caption{
        Representation of the scenario described in \Cref{sec:small-scale-crowd-alert}.
        graph dots represent wearables,
        and arcs lenghts represent the distance between them.
        %
        The rectangle at the bottom represents the monitor.
        %
        The closer the wearables are, the higher is the alert level
        (reddish tones).
        %
        \meta{NICOLAS riduci lo spazio vuoto fra i tre casi, così da guadagnare spazio. La legenda potrebbe essere messa sotto o sopra per guadagnarne di ulteriore}
    }
    \label{fig:crowd-alert}
\end{figure}

The system is composed of two kinds of device: \emph{wearable} and \emph{alert}.
%
Wearables consist of the following pulverised components:
sensors ($\sigma^w$), perceiving other devices by their signal strenght;
behaviour ($\beta^w$), converting raw data from the sensor into messages for the alert system; and
communication ($\chi^w$) sending data to the alert system.
%
They do not need state nor actuators.
%
The alert consists of the following pulverized components:
$\beta^a$, computing the mean distance among devices;
$\kappa^a$ \meta{
    NICOLAS what does this do? write within this meta block
};
$\chi^a$, responsible for receiving the data from the wearable devices;
$\alpha^a$, enacting the alarm by showing a color on the screen.
%
It needs no sensors.
